\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
% These three packages are from the American Mathematical Society and includes all of the important symbols and operations 
\usepackage{fullpage}
\usepackage{lipsum}
\usepackage{xfrac}
\usepackage{pgfplots}
\usepackage{titlesec}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{siunitx}
\usepackage{changepage}
\usepackage{cancel}
\usepackage{tikz}
\usetikzlibrary{arrows}
\pgfmathdeclarefunction{gauss}{2}{%
  \pgfmathparse{1/(#2*sqrt(2*pi))*exp(-((x-#1)^2)/(2*#2^2))}%
}


\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
% By default, an article has some vary large margins to fit the smaller page format.  This allows us to use more standard margins.

%\setlength{\parskip}{1em}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{3pt}
\renewcommand{\vec}[1]{\mathbf{#1}}
\linespread{1.75}

% This gives us a full line break when we write a new paragraph
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\title{Randomness and Computation: Written Problem Set 1}
\author{John Marangola}
\date{February 26, 2021}
\begin{document}
\maketitle

%CONSTANTS USED FOR PHYSICS COMPUTATIONS MADE BY ME TO MAKE LIFE EASIER!
% constant term for coulumb's law and electric field 1/4pi epsilon<0>:
\newcommand{\ec}{\frac{1}{4\pi\epsilon_0}}
%for problem 13:
\newcommand{\qa}{\frac{q^2}{a^2}}
% Standard basis vectors: ---------------->
\newcommand{\ih}{\hat{i}}
\newcommand{\jh}{\hat{j}}
\newcommand{\kh}{\hat{k}}
%--------------------------------------------------
% Differentiation at a point:
\newcommand{\at}[2][]{#1|_{#2}}
\section*{1.}
    \begin{enumerate}
        \item[(a)]
        \begin{equation}
            b(n, p, k) = \binom{n}{k}p^{k}\left(1-p\right)^{n-k}
        \end{equation}
        \begin{flushleft}
        
            Under the assumption that Latouch has the ability that she claims, the sample space $\Omega$ is given by the number of times Latouch guesses correctly:
        \end{flushleft}
        \begin{equation*}
            \Omega = \{0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10\}, \text{ such that} \; m(\omega)=b(10, 0.75, \omega) \; \forall \omega\in\Omega 
        \end{equation*}
        \begin{flushleft}
            Let $E_1$ be the event that Latouch wins the bet such that:
        \end{flushleft}
        \begin{center}
            $E_1 = \{7, 8, 9, 10\}$
        \end{center}
        \begin{align*}
            P(E_1) &= \sum_{k=7}^{10}{b(10, 0.75, k)} = \sum_{k=7}^{10}{\binom{10}{k}(0.75)^{k}\left(0.25\right)^{10-k}} \\
            &= \binom{10}{7}(0.75)^7 (0.25)^3 +\text{ ... } + \binom{10}{10}(0.75)^{10} \\
            P(E_1) &= 0.7758750916 \approx 0.776
        \end{align*}
        \item[(b)] Now, assume that Latouch is bluffing. If Latouch has no special ability, the probability that she makes a single guess correctly is 0.5. Likewise, the mean of the binomial distribution corresponding to the probabilities of X is given by $np=(10)(0.5)=5$. Letting $E_2$ be the event that Latouch loses the bet given that she is lying about her ability:
        \begin{align*}
            E_2 &= \{0, 1, 2, 3, 4, 5, 6\} \\
            P(E_2) &= \sum_{i=0}^6 b(10, 0.5, i) =0.828125\approx 0.828
        \end{align*}
    \end{enumerate}
\section*{2.}
    \begin{flushleft} 
        We define the null hypothesis $H_0$ to be that Dr. Venkman is guessing. It follows naturally that $\alpha$, $\beta$ are the probabilities of Type I and Type II errors, respectively. More precisely, $\alpha$ is the probability that $H_0$ is rejected when Dr. Venkman is simply guessing and $\beta$ is the probability that we fail to reject the null hypothesis when Dr. Venkman does indeed possess ultrasensory powers.
    \end{flushleft}
    \begin{center}
        From eqn (1) above, \\
        $\alpha(p) =  \sum\limits_{k=m}^{N}{b(N, p, k)}$, $\beta(p) = 1-\alpha(p)$\\
    Since $\overline{x}=np$, for N = 10 trials, the scenario above may be illustrated as: 
    \begin{tikzpicture}
        \begin{axis}[
          no markers, domain=2:10, samples=100,
          axis lines*=left, xlabel=$X$, ylabel=$p$,
          every axis y label/.style={at=(current axis.above origin),anchor=south},
          every axis x label/.style={at=(current axis.right of origin),anchor=west},
          height=6cm, width=12cm,
          %xtick={51,6.5}, 
          xtick={5, 7}, ytick=\empty,
          enlargelimits=false, clip=false, axis on top,
          grid = major
          ]
          \addplot [fill=cyan!20, draw=none, domain=5.85:6.75] {gauss(5,.5)}\closedcycle;
          %\addplot [fill=red!10, draw=none, domain=5:6] {gauss(7,.55)} \closedcycle;
          \addplot [very thick,cyan!50!black] {gauss(5,.5)};
          \addplot [very thick,cyan!50!black] {gauss(7,.5)};
        \node at (410,25) {$\alpha$};
        %\node at (385,25) {$\beta$};
        \end{axis}
        \end{tikzpicture}
        \begin{tikzpicture}
            \begin{axis}[
              no markers, domain=2:10, samples=100,
              axis lines*=left, xlabel=$X$, ylabel=$p$,
              every axis y label/.style={at=(current axis.above origin),anchor=south},
              every axis x label/.style={at=(current axis.right of origin),anchor=west},
              height=6cm, width=12cm,
              %xtick={51,6.5}, 
              xtick={5, 7}, ytick=\empty,
              enlargelimits=false, clip=false, axis on top,
              grid = major
              ]
              %\addplot [fill=cyan!20, draw=none, domain=5.85:6.75] {gauss(5,.5)}\closedcycle;
              \addplot [fill=red!10, draw=none, domain=5:6.15] {gauss(7,.55)} \closedcycle;
              \addplot [very thick,cyan!50!black] {gauss(5,.5)};
              \addplot [very thick,cyan!50!black] {gauss(7,.5)};
            %\node at (410,25) {$\alpha$};
            \node at (385,25) {$\beta$};
            \end{axis}
            \end{tikzpicture}
    \end{center}
\begin{flushleft}
To carry out a test such that the probability of making Type I, and II errors is less than 0.05, we must find a target number of guesses, m out of N that Dr. Venkman must guess correctly or incorrectly in order to ensure that $\alpha$, $\beta<0.05$. More precisely, 
\end{flushleft}
\begin{equation*}
    \alpha =  \sum\limits_{k=m}^{N}{b(N, p_0, k)} < 0.05, \beta = 1-\alpha(p_1) < 0.05\\
\end{equation*}
Assume that Dr. Venkman is indeed guessing as we suspect. If his true probability of guessing correctly $p_0$ = 0.5, we can find a target number of correct guesses m for some N trials such that:
\begin{equation*}
    \sum\limits_{k=m}^{N}{b(N, 0.5, k)} < 0.05
\end{equation*}
At this number of correct guesses, the probability that we are making a type I error in assesing Dr. Venkman's abilities would be less than 0.05. Likewise, if we assume he does have this ability, we can determine values for m, N such that:
\begin{equation*}
\beta(0.7) = 1-\alpha(0.7) < 0.05 \rightarrow 1 -  \sum\limits_{k=m}^{N}{b(N, 0.7, k)} < 0.05
\end{equation*}
In other words, if he guessed m times correctly in N trials, the probability of making a type II error and stating that he doesn't have this ability would be less than 0.05. Using N=100 trials, we compute this value numerically. Since increasing m will make $\alpha$ smaller and while decreasing m will make $\beta$ smaller, there is a range of m for which $\alpha, \beta < 0.05$ Numerically, it was found that for subjecting Dr. Venkman to N=100 trials m must be less than 62 for $\beta <0.05$ and m must be greater than 59 for $\alpha <0.05$.
Thus, we may devise a test that if $59 \leq X \leq 62 \rightarrow \alpha, \beta < 0.05$ and we reject the null hypothesis that he is making fradulent claims. Otherwise, we fail to reject $H_0$ as we do not possess adequate certainty about the result ie. $\max(\alpha, \beta) \geq 0.05$.
\end{document}
